Environment affects specialisation of plants and pollinators

### 2019-11-27 paper/manuscript.Rmd
Improve title

---
title: "Environmental stress affects niche breadth in plant-pollinator communities"
author: 
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
# csl: pnas.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument{supp-info}
  - \usepackage[export]{adjustbox}
  - \usepackage{caption}
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Environment affects specialisation of plants and pollinators"
author: 
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
# csl: pnas.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument{supp-info}
  - \usepackage[export]{adjustbox}
  - \usepackage{caption}
editor_options: 
  chunk_output_type: console
---
